---
title: "rsm_test"
author: "irw"
date: "1/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is a test of the RSM package and its use for running an experimental design.

It is adapted from the guide by the author, Russ Lenth. 
https://cran.r-project.org/web/packages/rsm/vignettes/rsm.pdf
https://cran.r-project.org/web/packages/rsm/rsm.pdf

```{r}
library(rsm)
library(tidyverse)
library(ggpubr)
```

Let's look at some of the data provided in the `rsm` package to see what a central composite design looks like. ChemReact was a dataset collected in 2 parts (blocks). First, the data in ChemReact1 was collected. Then the data from ChemReact2 was collected for further analysis.

```{r}
ChemReact
ggscatter(ChemReact1, "Time", "Temp")
ggscatter(ChemReact2, "Time", "Temp")
ggscatter(ChemReact, "Time", "Temp", color = "Block")
```

In order to use this data with the `rsm` functions, it has to be coded. The values of time are centered around 85 and vary by +/-5; with temperature, the values are centered about 175 +/- 5.

```{r}
CR1 <- coded.data(ChemReact1, x1 ~ (Time - 85)/5, x2 ~ (Temp - 175)/5)
CR1
tibble(CR1)
```


The `ccd.pick()` function describes available central composite designs based on the input parameters.
```{r}
ccd.pick(2)
```

The `ccd()` function shows the run order, treatments, and blocks in the central composite design selected.

```{r}
ccd(2)
```

The default behavior is to choose 4 replicates at the center. But from `ccd.pick()`, we can see that having one center point is an option.

```{r}
ccd(2, n0=1)
```


To make a response surface after defining the design and collecting the data, you have to first make a model.
```{r}
CR1.rsm <- rsm(Yield ~ FO(x1, x2), data = CR1)
summary(CR1.rsm)
```

This model should be avoided because of the low Lack of Fit p-value (~0.01). Take a look at the model for a two way interaction. This can be done by simply updating the model.
```{r}
CR1.rsmi <- update(CR1.rsm, . ~ . + TWI(x1, x2))
summary(CR1.rsmi)
```

Given the low Lack of Fit p-value, the model needs more data. Enter the second block. The `djoin` function will automatically code the variables and add the blocks.

```{r}
CR2 <- djoin(CR1, ChemReact2)
CR2
```

Now there is enough information to fit a second order model, but the blocks should be accounted for in the new model.
```{r}
CR2.rsm <- rsm(Yield ~ Block + SO(x1, x2), data = CR2)
summary(CR2.rsm)
```

